Simulation study

### 2022-03-22 Simulation/Simulation.Rmd

- number of observations ($n = \{50, 500, 5000\}$) *only max required*
- number of variables ($p = \{2\}$)
- coherence between variables ($r = \{0, 0.4, 0.8\}$)

@@

- imputation method (`meth` = {none, mean imputation, regression imputation, stochastic regression})
- number of imputations (`m` = {1, 5}) *only max required*
- number of iterations (`maxit` = 1, 5, 10) *use mice.mids to shorten runtime?*

>>>>

- number of observations ($n = \{50, 500, 5000\}$) *[for efficiency: only max required?]*
- number of variables ($p = \{2\}$)
- coherence between variables ($r = \{0, 0.4, 0.8\}$)

@@

- imputation method (`meth` = {none, mean imputation, regression imputation, stochastic regression})
- number of imputations (`m` = {1, 5}) *[for efficiency: only max required?]*
- number of iterations (`maxit` = 1, 5, 10) *[for efficiency: use mice.mids to shorten runtime?]*
